On the Design, Implementation and Use of Laziness in R

### 2019-08-15 report/paper-extra.Rmd
Move extra report data to main report and fix summarization script

    df
}

bar <- function(widths, total, labels) {
    options(device = cairo_pdf)
    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
    xmin <- cumsum(c(0, head(widths, -1)))
    df <- data.frame(
        xmin = xmin,
        xmax = cumsum(widths),
        ymin = -0.5,
        ymax = 0.5,
        fill = factor(1:length(widths)),
        label = labels,
        xmid = widths/2.0 + xmin,
        ymid = 0
    )

    plot <-
        df %>%
        ggplot() +
        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill)) +
        geom_text(aes(label = label, x = xmid, y = ymid), colour = "white") +
        scale_y_continuous() +
        scale_x_continuous(breaks = cumsum(widths),
                           labels = relative_labels,
                           sec.axis = sec_axis(trans = ~ . * total,
                                               breaks = cumsum(widths),
                                               labels = count_labels)) +
        theme(axis.text.y = element_blank(),
              axis.ticks = element_blank(),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              legend.position = "none") +
        labs(x = "", y = "")
plot
}

@@

```{r echo = TRUE, warning=FALSE, message=FALSE}
alien_promises_by_expression <- read_table("alien_promises_by_expression")
```

# Alien Promises

```{r, eval = TRUE, echo = FALSE}
alien_promises_by_expression %>%
datatable()
```

>>>>

    df
}
```

```{r echo = TRUE, warning=FALSE, message=FALSE}

@@

### 2019-08-15 report/paper.Rmd
Move extra report data to main report and fix summarization script

function_call_summary <- read_table("function_call_summary")
grouped_object_count_by_type <- read_table("grouped_object_count_by_type")
argument_promise_count_by_value_type <- read_table("argument_promise_count_by_value_type")
argument_promise_count_by_expression_type <- read_table("argument_promise_count_by_expression_type")
promise_count_by_category <- read_table("promise_count_by_category")
argument_promise_count_by_dispatch_type <- read_table("argument_promise_count_by_dispatch_type")
argument_promise_count_by_force_count <- read_table("argument_promise_count_by_force_count")
package_strictness <- read_table("package_strictness")
formal_parameter_count_by_use <- read_table("formal_parameter_count_by_use")
argument_nature <- read_table("promise_argument_count_by_nature")
formal_parameter_count_by_usage_class <- read_table("formal_parameter_count_by_usage_class")
argument_promise_count_by_value_lookup_count <- read_table("argument_promise_count_by_value_lookup_count")
execution_times <- read_table("execution_times")
call_by_escape_and_type <- read_table("function_call_count_by_escape_category_and_return_value_type")
escaped_argument_count_by_nature <- read_table("escaped_argument_count_by_nature")
argument_promise_use_distribution <- read_table("argument_promise_use_distribution")
package_metaprogramming <- read_table("package_metaprogramming")
argument_expression_type_by_usage_class <- read_table("argument_expression_type_by_usage_class")
force_orders <- read_table("closure_count_by_force_order_count")
extreme_event_counts <- read_table("extreme_event_counts")
event_processing_rates <- read_table("event_processing_rates")
argument_type <- read_table("argument_count_by_type")
closure_count_by_call_count <- read_table("closure_count_by_call_count")
```

@@

dense_package_count <-
    package_function_distribution %>%
    filter(total_function_count > 50) %>%
    pull(relative_package_count) %>%
    sum()

package_function_distribution <-
    package_function_distribution %>%
    filter(total_function_count <= 50) %>%
    mutate(total_function_count = as.character(total_function_count)) %>%
    add_row(total_function_count = "> 50", relative_package_count = dense_package_count)

package_function_graph <-
    package_function_distribution %>%
    ggplot(aes(x = total_function_count, y = relative_package_count)) +
    geom_col() + 
    #coord_flip() +
    scale_x_discrete(limits = c(1:50, "> 50")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "")

save_local_graph(package_function_graph, "package_function.pdf", width = 12, height = 3)
```

@@

save_local_graph(closure_call_distribution_graph, "closure_call_distribution_graph.pdf", width = 12, height = 3)
```

@@

save_local_graph(closure_parameter_distribution_graph, "closure_parameter_distribution_graph.pdf", width = 12, height = 3)
```

@@

>>>>

bar <- function(widths, total, labels) {
    options(device = cairo_pdf)
    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
    xmin <- cumsum(c(0, head(widths, -1)))
    df <- data.frame(
        xmin = xmin,
        xmax = cumsum(widths),
        ymin = -0.5,
        ymax = 0.5,
        fill = factor(labels), #factor(1:length(widths)),
        label = labels,
        xmid = widths/2.0 + xmin,
        ymid = 0
    )

    plot <-
        df %>%
        ggplot() +
        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill)) +
        geom_text(aes(label = label, x = xmid, y = ymid), colour = "white") +
        scale_y_continuous() +
        scale_x_continuous(breaks = cumsum(widths),
                           labels = relative_labels,
                           sec.axis = sec_axis(trans = ~ . * total,
                                               breaks = cumsum(widths),
                                               labels = count_labels)) +
        theme(axis.text.y = element_blank(),
              axis.ticks = element_blank(),
              panel.grid.minor = element_blank(),
              panel.grid.major = element_blank(),
              legend.position = "none") +
        labs(x = "", y = "")
plot
}

function_call_summary <- read_table("function_call_summary")
grouped_object_count_by_type <- read_table("grouped_object_count_by_type")
argument_promise_count_by_value_type <- read_table("argument_promise_count_by_value_type")
argument_promise_count_by_expression_type <- read_table("argument_promise_count_by_expression_type")
promise_count_by_category <- read_table("promise_count_by_category")
argument_promise_count_by_dispatch_type <- read_table("argument_promise_count_by_dispatch_type")
argument_promise_count_by_force_count <- read_table("argument_promise_count_by_force_count")
package_strictness <- read_table("package_strictness")
formal_parameter_count_by_use <- read_table("formal_parameter_count_by_use")
argument_nature <- read_table("promise_argument_count_by_nature")
formal_parameter_count_by_usage_class <- read_table("formal_parameter_count_by_usage_class")
argument_promise_count_by_value_lookup_count <- read_table("argument_promise_count_by_value_lookup_count")
execution_times <- read_table("execution_times")
call_by_escape_and_type <- read_table("function_call_count_by_escape_category_and_return_value_type")
escaped_argument_count_by_nature <- read_table("escaped_argument_count_by_nature")
argument_promise_use_distribution <- read_table("argument_promise_use_distribution")
package_metaprogramming <- read_table("package_metaprogramming")
argument_expression_type_by_usage_class <- read_table("argument_expression_type_by_usage_class")
force_orders <- read_table("closure_count_by_force_order_count")
extreme_event_counts <- read_table("extreme_event_counts")
event_processing_rates <- read_table("event_processing_rates")
argument_type <- read_table("argument_count_by_type")
closure_count_by_call_count <- read_table("closure_count_by_call_count")
argument_promise_count_by_call_depth <- read_table("argument_promise_count_by_call_depth")
argument_promise_count_by_call_depth_and_expression_type <- read_table("argument_promise_count_by_call_depth_and_expression_type")
argument_promise_count_by_forcing_scope <- read_table("argument_promise_count_by_forcing_scope")

event_counts <- read_table("event_counts")
summarized_event_counts <- 
    read_table("summarized_event_counts") %>%
    arrange(desc(count))

extreme_event_counts <- read_table("extreme_event_counts")
event_processing_rates <- read_table("event_processing_rates")

substitute_class_summary <- read_table("substitute_class_summary")
non_same_scope_substitute_calls <- read_table("non_same_scope_substitute_calls")

promise_lifecycle_summary <- read_table("promise_lifecycle_summary")
promise_lifecycle_list <- read_table("promise_lifecycle_list")

context_sensitive_lookup_summary <- read_table("context_sensitive_lookup_summary")
context_sensitive_lookup_symbols <- read_table("context_sensitive_lookup_symbols")

promise_gc_summary <- read_table("promise_gc_summary")
promise_gc_distribution_by_type <- read_table("promise_gc_distribution_by_type")

promise_argument_forced_by_promise_argument <- read_table("promise_argument_forced_by_promise_argument")
promise_argument_returning_non_locally <- read_table("promise_argument_returning_non_locally")

created_side_effects <- read_table("created_side_effects")
observed_side_effects <- read_table("observed_side_effects")
```

@@

dense_package_count <-
    package_function_distribution %>%
    filter(total_function_count > 10) %>%
    pull(relative_package_count) %>%
    sum()

package_function_distribution <-
    package_function_distribution %>%
    filter(total_function_count <= 10) %>%
    mutate(total_function_count = as.character(total_function_count)) %>%
    add_row(total_function_count = "> 10", relative_package_count = dense_package_count)

package_function_graph <-
    package_function_distribution %>%
    ggplot(aes(x = total_function_count, y = relative_package_count)) +
    geom_col() + 
    coord_flip() +
    scale_x_discrete(limits = c(1:10, "> 10")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_package_count, labels=count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "")

save_local_graph(package_function_graph, "package_function.pdf", width = 12, height = 3)

PercSingleFunctionPackages <-
    package_function_distribution %>%
    filter(total_function_count == "1") %>%
    pull(relative_package_count)

generate_macro("PercSingleFunctionPackages", PercSingleFunctionPackages)

PercManyFunctionPackages <-
    package_function_distribution %>%
    filter(total_function_count == "> 10") %>%
    pull(relative_package_count)

generate_macro("PercManyFunctionPackages", PercManyFunctionPackages)    
```

@@

save_local_graph(closure_call_distribution_graph, "closure_call_distribution_graph.pdf", width = 12, height = 3)

PercSingleCallClosures <-
    closure_count_by_call_count %>%
    filter(call_count == "1") %>%
    pull(relative_closure_count)

generate_macro("PercSingleCallClosures", PercSingleCallClosures)

PercManyCallClosures <-
    closure_count_by_call_count %>%
    filter(call_count == "> 10") %>%
    pull(relative_closure_count)

generate_macro("PercManyCallClosures", PercManyCallClosures)    
```

@@

save_local_graph(closure_parameter_distribution_graph, "closure_parameter_distribution_graph.pdf", width = 12, height = 3)

PercSingleParameterClosures <-
    closure_count_by_formal_parameter_count %>%
    filter(formal_parameter_count == "1") %>%
    pull(relative_closure_count)

generate_macro("PercSingleParameterClosures", PercSingleParameterClosures)

PercManyParameterClosures <-
    closure_count_by_formal_parameter_count %>%
    filter(formal_parameter_count == "> 5") %>%
    pull(relative_closure_count)

generate_macro("PercManyParameterClosures", PercManyParameterClosures)

maximum_parameter_function <-
    function_call_summary %>%
    arrange(desc(formal_parameter_count)) %>%
    slice(1)

CodeMaximumParameterFunctionName <-    
    maximum_parameter_function %>%
    pull(function_name) %>%
    str_sub(2, -2)

generate_macro("CodeMaximumParameterFunctionName", CodeMaximumParameterFunctionName)

CountMaximumParameterCount <-
    maximum_parameter_function %>%
    pull(formal_parameter_count)

generate_macro("CountMaximumParameterCount", CountMaximumParameterCount)
```

@@

# Events

```{r, eval = TRUE, echo = FALSE}
datatable(summarized_event_counts)

event_graph <-
    bar(summarized_event_counts$count, sum(summarized_event_counts$count), summarized_event_counts$event)

save_local_graph(event_graph, "event_graph.pdf", width=12, height=2.5)
```

# Substitute Summary

```{r, eval = TRUE, echo = FALSE}
datatable(substitute_class_summary)

PercCallerEnvSubstituteCalls <-
    substitute_class_summary %>%
    filter(substitute_class == "SameScope") %>%
    pull(relative_call_count)
generate_macro("PercCallerEnvSubstituteCalls", PercCallerEnvSubstituteCalls)

PercNewEnvSubstituteCalls <-
    substitute_class_summary %>%
    filter(substitute_class == "NewScope") %>%
    pull(relative_call_count)
generate_macro("PercNewEnvSubstituteCalls", PercNewEnvSubstituteCalls)

CountDynamicEnvSubstituteCalls <-
    substitute_class_summary %>%
    filter(substitute_class %in% c("DynamicScope", "StaticScope")) %>%
    pull(call_count) %>%
    sum()
generate_macro("CountDynamicEnvSubstituteCalls", CountDynamicEnvSubstituteCalls)

datatable(non_same_scope_substitute_calls)
```

# Promise Lifecycle

```{r, eval = TRUE, echo = FALSE}
alphabetical_row_names = c(letters, toupper(letters))

datatable(promise_lifecycle_summary)

CountLifecycleTotal <-
    promise_lifecycle_summary %>% 
    pull(total_lifecycle_count) %>%
    first()

generate_macro("CountLifecycleTotal", CountLifecycleTotal)

CountLifecycleUnescapedArguments <-
    promise_lifecycle_summary %>% 
    filter(argument, !escaped) %>% 
    pull(lifecycle_count)

generate_macro("CountLifecycleUnescapedArguments", CountLifecycleUnescapedArguments)

CountLifecycleEscapedArguments <-
    promise_lifecycle_summary %>% 
    filter(argument, escaped) %>% 
    pull(lifecycle_count)

generate_macro("CountLifecycleEscapedArguments", CountLifecycleEscapedArguments)

CountLifecycleNonArguments <-
    promise_lifecycle_summary %>% 
    filter(!argument) %>% 
    pull(lifecycle_count)

generate_macro("CountLifecycleNonArguments", CountLifecycleNonArguments)

decode_sequence <- function(seq) {
        unlist(str_split(str_sub(seq, 2, -2), " "))
}

expand_lifecycle <- function(action, count) {
    if(action == "()") {
        ""
    } else {
        action_seq <- decode_sequence(action)
        count_seq <- decode_sequence(count)
        str_c(rep(action_seq, count_seq), collapse = "")
    }
}

promise_lifecycle_list <-
    promise_lifecycle_list %>%
    mutate(event = map2_chr(action, count, expand_lifecycle)) %>%
    select(-action, -count, -promise_count)

escaped_argument_list <-
    promise_lifecycle_list %>%
    filter(argument, escaped)

datatable(escaped_argument_list)

escaped_argument_list %>%
    select(event, relative_promise_count) %>%
    arrange(desc(relative_promise_count)) %>%
    slice(1:7) %>%
    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
    pmap(function(event, relative_promise_count, index) {
        name <- str_c("TextLifecycleEscapedArguments", index)
        generate_macro(name, event)
        name <- str_c("PercLifecycleEscapedArguments", index)
        generate_macro(name, relative_promise_count)
    })

unescaped_argument_list <-
    promise_lifecycle_list %>%
    filter(argument, !escaped)

datatable(unescaped_argument_list)

unescaped_argument_list %>%
    select(event, relative_promise_count) %>%
    arrange(desc(relative_promise_count)) %>%
    slice(1:7) %>%
    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
    pmap(function(event, relative_promise_count, index) {
        name <- str_c("TextLifecycleUnescapedArguments", index)
        generate_macro(name, event)
        name <- str_c("PercLifecycleUnescapedArguments", index)
        generate_macro(name, relative_promise_count)
    })

non_argument_list <-
    promise_lifecycle_list %>%
    filter(!argument)

datatable(non_argument_list)

non_argument_list %>%
    select(event, relative_promise_count) %>%
    arrange(desc(relative_promise_count)) %>%
    slice(1:6) %>%
    mutate(index = alphabetical_row_names[dplyr::row_number()]) %>%
    pmap(function(event, relative_promise_count, index) {
        name <- str_c("TextLifecycleNonArguments", index)
        generate_macro(name, event)
        name <- str_c("PercLifecycleNonArguments", index)
        generate_macro(name, relative_promise_count)
    })

# Context Sensitive Lookup

```{r, eval = TRUE, echo = FALSE}
datatable(context_sensitive_lookup_summary)

context_sensitive_binding_lookup <- 
    context_sensitive_lookup_summary %>%
    pull(binding_lookup) %>%
    sum()
generate_macro("CountConSenBndgLkp", context_sensitive_binding_lookup)

context_sensitive_argument_binding_lookup_failure <- 
    context_sensitive_lookup_summary %>%
    filter(argument & !success) %>%
    pull(binding_lookup) %>%
    sum()
generate_macro("CountConSenArgBndgLkpFailure", context_sensitive_argument_binding_lookup_failure)

context_sensitive_argument_force <-
    context_sensitive_lookup_summary %>% 
    filter(argument) %>% 
    pull(forced) %>% 
    sum()
generate_macro("CountConSenArgForce", context_sensitive_argument_force)

context_sensitive_argument_force_successful <-
    context_sensitive_lookup_summary %>% 
    filter(argument & success) %>% 
    pull(forced) %>% 
    sum()
generate_macro("CountConSenArgForceSuccess", context_sensitive_argument_force_successful)
generate_macro("PercConSenArgForceSuccess", context_sensitive_argument_force_successful/context_sensitive_argument_force)

context_sensitive_argument_force_failure <-
    context_sensitive_lookup_summary %>% 
    filter(argument & !success) %>% 
    pull(forced) %>% 
    sum()
generate_macro("CountConSenArgForceFailure", context_sensitive_argument_force_failure)
generate_macro("PercConSenArgForceFailure", context_sensitive_argument_force_failure / context_sensitive_argument_force)

context_sensitive_lookup_symbols <-
    context_sensitive_lookup_symbols %>%
    filter(formal_parameter_position != -1)

symbol_overload_table <-
    context_sensitive_lookup_symbols %>%
    filter(argument) %>%
    group_by(symbol) %>%
    summarize(count = n_distinct(function_id, formal_parameter_position)) %>%
    ungroup() %>%
    arrange(desc(count))

context_sensitive_overloaded_parameter_count <-
    context_sensitive_lookup_symbols %>%
    distinct(function_id, formal_parameter_position) %>%
    nrow()
generate_macro("CountConSenParameter", context_sensitive_overloaded_parameter_count)

context_sensitive_overloaded_function_count <-
    context_sensitive_lookup_symbols %>%
    distinct(function_id) %>%
    nrow()
generate_macro("CountConSenFunction", context_sensitive_overloaded_function_count)

row_names <- c(letters, toupper(letters))

symbol_overload_table %>%
    slice(1:30) %>%
    mutate(index = row_names[dplyr::row_number()]) %>%
    pmap(function(index, symbol, count) {
        generate_macro(paste0("CodeConSenSymbol", index), symbol)
        generate_macro(paste0("CountConSenSymbol", index), count)
    })

datatable(symbol_overload_table)
```

# Promise GC

```{r, eval = TRUE, echo = FALSE}
datatable(promise_gc_summary)

AllGcPromises <-
    promise_gc_summary %>%
    pull(promise_count) %>%
    sum()

CountSingleGcPromises <-
    promise_gc_summary %>%
    filter(single_gc_cycle) %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercSingleGCPromises", CountSingleGcPromises/AllGcPromises)

CountMultipleGcPromises <-
    promise_gc_summary %>%
    filter(!single_gc_cycle) %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercMultipleGcPromises", CountMultipleGcPromises/AllGcPromises)

CountMultipleGcEscapedArgumentPromises <-
    promise_gc_summary %>%
    filter(!single_gc_cycle & escaped & argument) %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercMultipleGcEscapedArgumentPromises", CountMultipleGcEscapedArgumentPromises/CountMultipleGcPromises)

CountMultipleGcUnescapedArgumentPromises <-
    promise_gc_summary %>%
    filter(!single_gc_cycle & argument & !escaped) %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercMultipleGcUnescapedArgumentPromises", CountMultipleGcUnescapedArgumentPromises/CountMultipleGcPromises)

CountMultipleGcNonArgumentPromises <-
    promise_gc_summary %>%
    filter(!single_gc_cycle & !argument) %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercMultipleGcNonArgumentPromises", CountMultipleGcNonArgumentPromises/CountMultipleGcPromises)

datatable(promise_gc_distribution_by_type)
```

# Side Effects

```{r, eval = TRUE, echo = FALSE}

CountEffectPromises <-
    created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("CountEffectPromises", CountEffectPromises)

CountEffectSamePromises <-
    created_side_effects %>%
    filter(mode == "S") %>%
    pull(count) %>%
    sum()

generate_macro("CountEffectSamePromises", CountEffectSamePromises)
generate_macro("PercEffectSamePromises", CountEffectSamePromises / CountEffectPromises)

CountEffectOtherPromises <-
    created_side_effects %>%
    filter(mode == "O") %>%
    pull(count) %>%
    sum()

generate_macro("CountEffectOtherPromises", CountEffectOtherPromises)
generate_macro("PercEffectOtherPromises", CountEffectOtherPromises / CountEffectPromises)

CountEffectLexicalPromises <-
    created_side_effects %>%
    filter(mode == "L") %>%
    pull(count) %>%
    sum()

generate_macro("CountEffectLexicalPromises", CountEffectLexicalPromises)
generate_macro("PercEffectLexicalPromises", CountEffectLexicalPromises / CountEffectPromises)
```
## Direct & Same Environment

```{r, eval = TRUE, echo = FALSE}

direct_S_created_side_effects <-
    created_side_effects %>%
    filter(direct & mode == "S") %>%
    arrange(desc(count))

datatable(direct_S_created_side_effects)

CountEffectDirectSamePromises <-
    direct_S_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectDirectSamePromises", CountEffectDirectSamePromises / CountEffectSamePromises)
```

## Indirect & Same Environment

```{r, eval = TRUE, echo = FALSE}
indirect_S_created_side_effects <-
    created_side_effects %>%
    filter(!direct & mode == "S") %>%
    arrange(desc(count))

datatable(indirect_S_created_side_effects)

CountEffectIndirectSamePromises <-
    indirect_S_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectIndirectSamePromises", CountEffectIndirectSamePromises / CountEffectSamePromises)
```

## Direct & Other Environment

```{r, eval = TRUE, echo = FALSE}
direct_O_created_side_effects <-
    created_side_effects %>%
    filter(direct & mode == "O") %>%
    arrange(desc(count))

datatable(direct_O_created_side_effects)

CountEffectDirectOtherPromises <-
    direct_O_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectDirectOtherPromises", CountEffectDirectOtherPromises / CountEffectOtherPromises)
```

## Indirect & Other Environment

```{r, eval = TRUE, echo = FALSE}
indirect_O_created_side_effects <-
    created_side_effects %>%
    filter(!direct & mode == "O") %>%
    arrange(desc(count))

datatable(indirect_O_created_side_effects)

CountEffectIndirectOtherPromises <-
    indirect_O_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectIndirectOtherPromises", CountEffectIndirectOtherPromises / CountEffectOtherPromises)
```

## Direct & Lexical Parent Environment

```{r, eval = TRUE, echo = FALSE}
direct_L_created_side_effects <-
    created_side_effects %>%
    filter(direct & mode == "L") %>%
    arrange(desc(count))

datatable(direct_L_created_side_effects)

CountEffectDirectLexicalPromises <-
    direct_L_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectDirectLexicalPromises", CountEffectDirectLexicalPromises / CountEffectLexicalPromises)
```

## Indirect & Lexical Parent Environment

```{r, eval = TRUE, echo = FALSE}
indirect_L_created_side_effects <-
    created_side_effects %>%
    filter(!direct & mode == "L") %>%
    arrange(desc(count))

datatable(indirect_L_created_side_effects)

CountEffectIndirectLexicalPromises <-
    indirect_L_created_side_effects %>%
    pull(count) %>%
    sum()

generate_macro("PercEffectIndirectLexicalPromises", CountEffectIndirectLexicalPromises / CountEffectLexicalPromises)
```
##datatable(observed_side_effects)
```

# Evaluation Call Depth

```{r, eval = TRUE, echo = FALSE}

datatable(argument_promise_count_by_call_depth)

## remove non-argument and escaped promises
argument_promise_count_by_call_depth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth != "-1")

CountPromiseAllDepth <-
    argument_promise_count_by_call_depth %>%
    pull(promise_count) %>%
    sum()

CountPromiseZeroDepth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth == "0") %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercPromiseZeroDepth", CountPromiseZeroDepth / CountPromiseAllDepth)

CountPromiseOneDepth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth == "1") %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercPromiseOneDepth", CountPromiseOneDepth / CountPromiseAllDepth)

CountPromiseMultipleDepth <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth != "0" & call_depth != "1") %>%
    pull(promise_count) %>%
    sum()
generate_macro("PercPromiseMultipleDepth", CountPromiseMultipleDepth / CountPromiseAllDepth)

total_count <-  sum(argument_promise_count_by_call_depth$promise_count)

argument_promise_call_depth_graph <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth %in% c(1:5, "> 5")) %>%
    ggplot(aes(call_depth, relative_promise_count)) +
    geom_col() +
    scale_x_discrete(limits = c(1:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
                                           labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip()

save_local_graph(argument_promise_call_depth_graph, "forcedepth.pdf", width=12, height=2.5)

datatable(argument_promise_count_by_call_depth_and_expression_type)

CountPromiseFunctionCallCallerEvaluation <-
    argument_promise_count_by_call_depth_and_expression_type %>%
    filter(call_depth == 0 & expression_type == "Function Call") %>%
    pull(promise_count) %>%
    sum()

generate_macro("PercPromiseFunctionCallCallerEvaluation", 
                CountPromiseFunctionCallCallerEvaluation / CountArgumentPromiseExpressionFunctionCall)

CountPromiseFunctionCallRemoteEvaluation <-
    argument_promise_count_by_call_depth_and_expression_type %>%
    filter(call_depth != 0 & expression_type == "Function Call") %>%
    pull(promise_count) %>%
    sum()

generate_macro("PercPromiseFunctionCallRemoteEvaluation", 
                CountPromiseFunctionCallRemoteEvaluation / CountArgumentPromiseExpressionFunctionCall)    
CountPromiseFunctionCallAllEvaluation <-
    argument_promise_count_by_call_depth_and_expression_type %>%
    filter(expression_type == "Function Call") %>%
    pull(promise_count) %>%
    sum()

generate_macro("PercPromiseFunctionCallNonEvaluation", 
                (CountArgumentPromiseExpressionFunctionCall - CountPromiseFunctionCallAllEvaluation) / CountArgumentPromiseExpressionFunctionCall)
```

# Mutually Forcing Argument Promises

```{r, eval = TRUE, echo = FALSE}
datatable(promise_argument_forced_by_promise_argument)

CountMutualForcing <-
    sum(promise_argument_forced_by_promise_argument$count)

generate_macro("CountMutualForcing", CountMutualForcing)

CountMutualForcingFunctions <-
    n_distinct(promise_argument_forced_by_promise_argument$function_id)

generate_macro("CountMutualForcingFunctions", CountMutualForcingFunctions)

CountMutualForcingArgumentPositions <-
    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
               promise_argument_forced_by_promise_argument$forcing_actual_argument_position)

generate_macro("CountMutualForcingArgumentPositions", CountMutualForcingArgumentPositions)

CountMutualForcedArgumentPositions <-
    n_distinct(promise_argument_forced_by_promise_argument$function_id, 
               promise_argument_forced_by_promise_argument$formal_parameter_position)

generate_macro("CountMutualForcedArgumentPositions", CountMutualForcedArgumentPositions)
```

# Non local returning promises

```{r, eval = TRUE, echo = FALSE}
datatable(promise_argument_returning_non_locally)

CountNonLocalFunctions <-
    promise_argument_returning_non_locally %>%
    distinct(function_id) %>%
    nrow()
generate_macro("CountNonLocalFunctions", CountNonLocalFunctions)

CountNonLocalArguments <-
    promise_argument_returning_non_locally %>%
    pull(count) %>%
    sum
generate_macro("CountNonLocalArguments", CountNonLocalArguments)

# Promise Dispatch Force

```{r, eval = TRUE, echo = FALSE}

s3_promise_force <-
    argument_promise_count_by_forcing_scope %>%
    filter(forcing_scope == "S3") %>%
    pull(promise_count) %>%
    sum()
generate_macro("CountSThreePromiseForce", s3_promise_force)

s4_promise_force <-
    argument_promise_count_by_forcing_scope %>%
    filter(forcing_scope == "S4") %>%
    pull(promise_count) %>%
    sum()
generate_macro("CountSFourPromiseForce", s4_promise_force)

datatable(argument_promise_count_by_forcing_scope)
```

TODO:
- 1. Promise Evaluation Depth
- 2. Mutually forcing argument promises
- 3. Non local returning promise arguments
- 4. Validation of these cases
- 5. Fix Side Effect data and analysis
- 6. Number of promises forced by dispatch
- 7. Kind of expression in unbound promises

- 9. Add event count bar
- 8. Add time measurement to all R analyses
- 12. Move summarize outliers form summary.R to the analysis report.
      Add summarize outliers line to the report and make sure the analysis is correct.

- 10. Add figure showing data/files/time at each step of analysis
- 11. Add figure showing how reduce/combine etc. work
